\startappendix{Web-based Information Discovery and Curation Tools}
\label{chapter:appendix_tools}

The results of Web tool evaluations that were conducted using the preliminary framework are summarized in Table~\ref{table:tool_summaries}.

\begin{longtable}{|p{0.16\linewidth}| p{0.30\linewidth}| p{0.50\linewidth}|}
\caption{Summaries of Web-based Information Discovery and Curation Tools Evaluations}
\label{table:tool_summaries} \\

\hline
Application     & Description                                                                  & Summary of findings                                                                                                                                                                                                                                                                                            
\\
\hline
Pinterest       & \raggedright
Visual discovery tool, available at www.pinterest.com                        &
-\hspace{0.4cm}Supports serendipitous browsing, bookmark-based rediscovery, channel-based information discovery, and information curation. 


-\hspace{0.4cm}Lacks support for search- and history-based rediscovery and fact finding.                                                                       \\
\hline
Delicious       & \raggedright
Social bookmarking service, available at delicious.com &                                                                -\hspace{0.4cm}Supports channel-based discovery, bookmark-based rediscovery, and supports social curation. 

-\hspace{0.4cm}Lacks support for visual link preview and list-based categorization. \\
\hline
Tumblr          & \raggedright Microblogging platform, available at www.tumblr.com                         &-\hspace{0.4cm}Supports serendipitous browsing, bookmark-based rediscovery, channel-based information discovery.

-\hspace{0.4cm}Lacks support for fact finding and list-based categorization.                                                                                                 \\
\hline
StumbleUpon     & \raggedright Web page discovery tool, available at www.stumbleupon.com                    & -\hspace{0.4cm}Supports serendipitous browsing, bookmark- and history-based information rediscovery, channel-based information discovery, and information curation. 

-\hspace{0.4cm}Lacks support for fact finding.                                                                       \\
\hline
Wikipedia       & \raggedright Free content Internet encyclopedia, available at en.wikipedia.org             & -\hspace{0.4cm}Supports serendipitous discovery, fact finding, search-based rediscovery.

-\hspace{0.4cm}Lacks support for history-based and bookmark-based rediscovery, personal preservation and resource evaluation. \\
\hline
Google Maps     & \raggedright Web mapping service, available at www.google.ca/maps                         & 
-\hspace{0.4cm}Supports fact finding and rediscovery. 

-\hspace{0.4cm}Lacks support for curation mechanisms, except for personal information preservation. 
\\
\hline
Rotten Tomatoes & \raggedright Movie and TV database, available at www.rottentomatoes.com                   & -\hspace{0.4cm}Supports fact discovery, serendipitous browsing, and search-based rediscovery. 

-\hspace{0.4cm}Lacks support for history-based and bookmark-based rediscovery, information preservation, and management. \\
\hline
500px           & \raggedright Photography site, available at 500px.com            & 
-\hspace{0.4cm}Supports serendipitous browsing, channel-based discovery, and social curation. 

-\hspace{0.4cm}Lacks support for fact discovery and list-based categorization. \\
\hline
BucketList      & \raggedright Goal tracking and discovery service, available at bucketlist.org             & -\hspace{0.4cm}Supports serendipitous discovery, bookmark-based rediscovery, and channel-based discovery. 

-\hspace{0.4cm}Lacks support for fact discovery, search- and history-based rediscovery. \\
\hline
We Heart It     & \raggedright Visual discovery tool, available at weheartit.com                            & -\hspace{0.4cm}Supports serendipitous browsing, bookmark-based rediscovery, channel-based information discovery, and information curation.

-\hspace{0.4cm}Lacks support for fact finding.                                                                       \\
\hline
Scoop.it!       & \raggedright Online publishing platform, available at www.scoop.it                        & -\hspace{0.4cm}Supports serendipitous browsing, bookmark-based information rediscovery, channel-based information discovery, and information curation. 

-\hspace{0.4cm}Lacks support for fact finding.                                                 \\
\hline
Google Images   & \raggedright Image discovery service, available at images.google.com                      & -\hspace{0.4cm}Supports serendipitous browsing. 

-\hspace{0.4cm}Lacks support for rediscovery, channel-based discovery, fact finding, or  information curation.                                                                                                         \\
\hline
Vimeo           & \raggedright Video sharing Website, available at vimeo.com                                & -\hspace{0.4cm}Supports serendipitous discovery, bookmark-based rediscovery, and channel-based discovery, and information curation. 

-\hspace{0.4cm}Lacks support for fact discovery and list-based categorization. \\
\hline
LifeHacker      & \raggedright Daily Weblog, available at lifehacker.com                                    & -\hspace{0.4cm}Supports serendipitous discovery. 

-\hspace{0.4cm}Lacks support for channel-based discovery and information curation.                                                                                                                                                                                                 \\
\hline
YouTube         & \raggedright Video hosting platform, available at www.youtube.com                         & -\hspace{0.4cm}Allows for serendipitous discovery, channel-based discovery, history- and bookmark-based revisitation, and information curation. 

-\hspace{0.4cm}Lacks support for internal sharing.                                                                                                                                                \\
\hline
Yelp            & \raggedright Business review site, available at www.yelp.ca                               & -\hspace{0.4cm}Supports fact finding, serendipitous browsing, search-based rediscovery, certain aspects of information curation (e.g., evaluation and annotation).                                                                                                

 -\hspace{0.4cm}Lacks support for channel-based discovery.   \\
\hline
IMDb            & \raggedright Movie database, available at www.imdb.com                                    & -\hspace{0.4cm}Supports fact discovery, serendipitous discovery, and rediscovery. 

-\hspace{0.4cm}Lacks support for channel-based discovery.                                                                                                                                                          \\
\hline
Trip Adviser    & \raggedright Travel site, available at www.tripadvisor.ca                                 & -\hspace{0.4cm}Supports serendipitous discovery, fact finding, and personal information curation. 

-\hspace{0.4cm}Lacks support for history-based rediscovery.                                                                                                                                 \\
\hline
Urban Spoon     & \raggedright Online bar and restaurant guide, available at www.urbanspoon.com             & -\hspace{0.4cm}Supports serendipitous browsing, fact finding, evaluation and annotations. 

-\hspace{0.4cm}Lacks support for channel-based discovery.  \\
\hline
Thesaurus       & \raggedright Online thesaurus, available at thesaurus.com                                 & -\hspace{0.4cm}Supports serendipitous browsing and fact discovery. 

-\hspace{0.4cm}Lacks support for information curation.                                                                                \\
\hline
\end{longtable}
